Machine Learning(ML) is leading to rapid advancements across many domains. Recent advancements have demonstrated that deep learning architectures are versatile and capable of solving a broad range of complex problems. The explosion of algorithms have lead to many different subfields each with their own advantage. In this white paper, we will focus on applications of machine learning where they are needed to run fast so as to solve critical scientific problems. We will discuss the myriad of scientific problems that require fast machine learning, and we will outline unifying themes across these domains that can lead to general solutions. Furthermore, we will review the current technology needed to make machine learning algorithms run fast, and we will present critical technological problems that, if solved, could lead to major scientific advancements. This paper is a review of the second annual Fast Machine Learning conference\cite{FMLConf2}, and will focus on the materials presented at this workshop. 

Much of the advancements within machine learning over the past few years has originated from the use of heterogeneous hardware. In particular, the use of GPUs has enabled the development of large deep learning algorithms.  The ability to build large AI algorithms has opened the possibility of deep learning algorithms that are capable of performing sophisticated tasks. In parallel with these developments, new types of deep learning algorithms have emerged which aim to reduce the number of multiplications, and we weight information so as to enable fast effective AI algorithms. 

As the tools have become more sophisticated, much of the focus has turned to building very large  algorithms that solve complicated problems, such as a language translation, and voice recognition. However, in the wake of these developments, a broad range of scientific applications have emerged that can be solved with the current existing technology. Many of these algorithms 

In this proposal, we focus on 

%Scientific challenges to require Fast ML


%How to make a dee
The origins

%look across the wide range of machine learning architectures and try to understand ho we can make machine learning algorithms run fast. 

%The challenge of fast machine learning falls in 